### 2021-05-12 manuscript.Rmd
Fix typos.

* __Definition of Exposures and Outcomes__: The primary exposure of interest was the distance from the patient (measured towards the wastewater sites). The primary outcome of interest was the detection of a culturable MDRO, including MRSA, _C.difficile_, vancomycin-resistant _Enterococcus_ (VRE), extended-spectrum beta-lactamase (ESBL) producing _Enterobacterales_, carbapenem-resistant <span style='background-color:lightcyan'>(CR)</span> _Enterobacterales_, _Acinetobacter_, or _Pseudomonas_. Secondary outcomes of interest included the detection of MDRO genera by 16S rRNA gene sequencing.<span style='background-color:lightcyan'> _C.difficile_ was included within the primary outcome of MDRO detection due to its importance as an HAI and prior evidence supporting environmental transmission.</span>

@@

* __Detection of MDROs in the Proximity to Patient-Associated MDROs__: We enrolled 51 patient rooms at the time of admitting a patient who had been recently diagnosed with MDRO colonization or infection by clinical culture <span style='background-color:lightcyan'>between November 4, 2019 and March 12, 2020, obtaining a median of 3 specimens per patient room (interquartile range (IQR) 4-6). Prior to patient entry, 75% of rooms (n=38) underwent terminal cleaning with ultraviolet germicidal irradiation (UVGI). All rooms received daily cleaning using Oxivir Plus, a hydrogen-peroxide cleaning product, with the exception of patients in _C. difficile_ isolation whose rooms were cleaned with bleach.</span> The most common enrolling isolate for patients included in the study was C.difficile (n=16, 31%), followed by ESBL-producing Enterobacterales (ESBL) (n=15, 29%), MRSA (n=13, 25%), VRE (n=7, 14%), and <span style='background-color:lightcyan'>CR</span> Gram-negative organisms (n=4, 8%). Across 51 subjects, we performed 136 sampling events, with each event collecting composite samples from three in-room sites (near, intermediate, and far), and each composite sample plated on six MDRO-selective media. **Table 1** shows the 11 MDROs identified across all enrolled subjects, the total number of times they were recovered from the healthcare environment, and frequency with which they were detected from cultured environmental specimens.

>>>>

* __Definition of Exposures and Outcomes__: The primary exposure of interest was the distance from the patient (measured towards the wastewater sites). The primary outcome of interest was the detection of a culturable MDRO, including MRSA, _C. difficile_, vancomycin-resistant _Enterococcus_ (VRE), extended-spectrum beta-lactamase (ESBL) producing _Enterobacterales_, carbapenem-resistant <span style='background-color:lightcyan'>(CR)</span> _Enterobacterales_, _Acinetobacter_, or _Pseudomonas_. Secondary outcomes of interest included the detection of MDRO genera by 16S rRNA gene sequencing.<span style='background-color:lightcyan'> _C. difficile_ was included within the primary outcome of MDRO detection due to its importance as an HAI and prior evidence supporting environmental transmission.</span>

@@

* __Detection of MDROs in the Proximity to Patient-Associated MDROs__: We enrolled 51 patient rooms at the time of admitting a patient who had been recently diagnosed with MDRO colonization or infection by clinical culture <span style='background-color:lightcyan'>between November 4, 2019 and March 12, 2020, obtaining a median of 3 specimens per patient room (interquartile range (IQR) 4-6). Prior to patient entry, 75% of rooms (n=38) underwent terminal cleaning with ultraviolet germicidal irradiation (UVGI). All rooms received daily cleaning using Oxivir Plus, a hydrogen-peroxide cleaning product, with the exception of patients in _C. difficile_ isolation whose rooms were cleaned with bleach.</span> The most common enrolling isolate for patients included in the study was C. difficile (n=16, 31%), followed by ESBL-producing Enterobacterales (ESBL) (n=15, 29%), MRSA (n=13, 25%), VRE (n=7, 14%), and <span style='background-color:lightcyan'>CR</span> Gram-negative organisms (n=4, 8%). Across 51 subjects, we performed 136 sampling events, with each event collecting composite samples from three in-room sites (near, intermediate, and far), and each composite sample plated on six MDRO-selective media. **Table 1** shows the 11 MDROs identified across all enrolled subjects, the total number of times they were recovered from the healthcare environment, and frequency with which they were detected from cultured environmental specimens.
